Analysis of pleiotropy of eQTLs

### 2023-01-19 presentation_230120_internal_seminar/intern_sem_230120.tex
ENH

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{The IRF1/IL4 locus}

        \begin{figure}[!]
            \includegraphics[width=0.95\textwidth]{fig/il4}
        \end{figure}

        \begin{itemize}
            \item Sevaral immune genes
            \item GWAS categories: allergic disease; autoimmune disease; body height; breast cancer; cancer; cardiovascular disease; hypertensive disorder; respiratory system disease; skin disease
            \item eQTL biosamples: adipose tissue;aorta;blood;brain;breast; ...
        \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{frame}
%    \frametitle{How are pleiotropic variants distributed?}
%
%    \begin{columns}
%        \begin{column}{0.32\textwidth}
%            \begin{center}
%                \includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
%            \end{center}
%        \end{column}
%        \begin{column}{0.32\textwidth}
%            \begin{center}
%                \includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
%            \end{center}
%        \end{column}
%        \begin{column}{0.32\textwidth}
%            \begin{center}
%                \includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
%            \end{center}
%        \end{column}
%    \end{columns}
%
%    \begin{center}
%        \includegraphics[width=\textwidth]{../presentation_230120_gold2022_paris/fig/chr5_131912097_132802472.png}
%    \end{center}
%
%    \small
%    \begin{itemize}
%        \item The cytokine locus: chr5:131,912,097-132,802,472. Genes IRF1, IL3, IL4, IL5, ...
%        \item Diseases: Allergy,Autoimmune dis.,Cancer of breast,Circulatory sys. dis.,Hypertension,Respiratory system dis.
%        \item For instance: rs2522051 regulates 12 e-genes in 23 e-tissues
%    \end{itemize}
%    \normalsize
%
%\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Do pleiotropic variants associate to more eQTL genes?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Do pleiotropic variants associate to more eQTL tissues?}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{How are pleiotropic variants distributed?}

    \begin{columns}
        \begin{column}{0.32\textwidth}
            \begin{center}
                \includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start132239645_end132497907_categories9.png}
            \end{center}
        \end{column}
        \begin{column}{0.32\textwidth}
            \begin{center}
                \includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start132239645_end132497907_categories9.png}
            \end{center}
        \end{column}
        \begin{column}{0.32\textwidth}
            \begin{center}
                \includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr5_start132239645_end132497907_categories9.png}
            \end{center}
        \end{column}
    \end{columns}

    \begin{center}
        \includegraphics[width=\textwidth]{../presentation_230120_gold2022_paris/fig/chr5_131912097_132802472.png}
    \end{center}

    \small
    \begin{itemize}
        \item The cytokine locus: chr5:131,912,097-132,802,472. Genes IRF1, IL3, IL4, IL5, ...
        \item Diseases: Allergy,Autoimmune dis.,Cancer of breast,Circulatory sys. dis.,Hypertension,Respiratory system dis.
        \item For instance: rs2522051 regulates 12 e-genes in 23 e-tissues
    \end{itemize}
    \normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Does trait categories correlate with eQTL and biosample counts?}

        \begin{figure}[!]
            \includegraphics[width=0.5\textwidth]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_egene_etissue_corr}\label{fig:count_per_rsid_gwas_egene_etissue_corr}
        \end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \begin{frame}
%        \frametitle{The IRF1/IL4 locus}
%
%        \begin{figure}[!]
%            \includegraphics[width=0.95\textwidth]{fig/il4}
%        \end{figure}
%
%        \begin{itemize}
%            \item Sevaral immune genes
%            \item GWAS categories: allergic disease; autoimmune disease; body height; breast cancer; cancer; cardiovascular disease; hypertensive disorder; respiratory system disease; skin disease
%            \item eQTL biosamples: adipose tissue;aorta;blood;brain;breast; ...
%        \end{itemize}
%
%    \end{frame}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Are pleiotropic variants associated to more eQTL genes?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Are pleiotropic variants associated to more eQTL tissues?}
